Reformulating phylogenetic mixed models to improve flexibility and speed

### 2018-09-24 main.tex
pushing pseudo results to finish the paper

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=1]{./git_push/ssplot.pdf}
  \caption{Old}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=1]{./git_push/plot.pdf}
  \caption{New}
\label{ssplot}
\end{figure}
\end{center}

@@

The full model (which matches the simulation model that incorporates phylogenetic signal on the intercept, slope and correlation) provides good estimates of the different levels of the phylogenetic variation signal (Figure 1 and 2). \bmb{delete ``signal''? or ``variation''? what does ``phylogenetic variation signal'' mean?}

>>>>

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=1]{./git_push/plot.Rout.pdf}
  \caption{New}
\label{ssplot}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=2]{./git_push/plot.Rout.pdf}
  \caption{New}
\label{ssplot}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=3]{./git_push/plot.Rout.pdf}
  \caption{New}
\label{ssplot}
\end{figure}
\end{center}

@@

The full model (which matches the simulation model that incorporates phylogenetic signal on the intercept, slope and correlation) provides good estimates for all parameters except for random correlation parameters
